RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-25 doc/paper.tex
Experiemntal evaluation: update

\subsection{Parameter tuning}
SAMO JEDAN PARAMETAR!!!
Zapravo dva parametra $penalty_{size}$ i $tolerance_{error}$ pri cemu je drugi manje vise zavistan od ocekivanog 
nivoa suma -- ne znam kako obrazloziti njegov tuning (mozda prema greski na trening skupu pa izabrati onaj za koji su R2 i RMSE bolji...).

\subsection{Comparison with other methods}

\begin{table}[!htb]
	\caption{Comparison without noise}\label{tab:comp_noise0}
	\centering
		\begin{tabular}{l|rrr|rrr} \hline
			& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
			RILS-ROLS&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
			AIFeynman&55.78&27.14&52.69&78.51&35.71&73.9\\
			GP-GOMEA&26.83&29.46&27.12&71.55&71.43&71.54\\
			AFP\_FE&26.98&20&26.23&59.05&28.57&55.77\\
			ITEA&22.41&7.14&20.77&27.59&21.43&26.93\\
			AFP&21.12&15.18&20.48&44.83&25&42.69\\
			DSR&19.72&19.64&19.71&25&14.29&23.85\\
			Operon&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
			gplearn&16.27&8.93&15.48&32.76&7.14&30\\
			SBP-GP&12.72&11.61&12.6&73.71&78.57&74.23\\
			EPLEX&12.39&8.93&12.02&46.98&21.43&44.23\\
			BSR&2.48&0.89&2.31&10.78&21.43&11.93\\
			FEAT&0&0.89&0.1&39.66&42.86&40\\
			FFX&0&0&0&0&0&0\\
			MRGP&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
			\hline
		\end{tabular}
\end{table}

>>>>

\subsection{Parameter tuning}
The \textsc{Rils}-\textsc{Rols} algorithms employs just two parameters that need to be tuned, $penalty_{size}$ and $tolerance_{error}$. The first parameter is set to 0.001(?), according to the preliminary experimental evaluation. The second parameter is tuned monitoring the two errors the algorithm produced on the training set; we choose a value for which a larger average $R^2$ and a smaller average RMSE error over all instances from the training set are produced. Note that the training set is chosen randomly with the cardinalty of ...

\fxnote{ drugi parametar manje vise zavistan od ocekivanog 
nivoa suma -- ne znam kako obrazloziti njegov tuning (mozda prema greski na trening skupu pa izabrati onaj za koji su R2 i RMSE bolji...). }

\subsection{Comparison with other methods}
\fxnote{Marko: TODO}
\begin{table}[!htb]
	\caption{Comparison without noise}\label{tab:comp_noise0}
	\centering
		\begin{tabular}{l|rrr|rrr} \hline
			& \multicolumn{3}{c|}{Exact model percentage} & \multicolumn{3}{c}{$R^2 > 0.999$ percentage}\\ \hline
			Method & Feynman & Strogatz & Total & Feynman & Strogatz & Total \\ \hline
			RILS-ROLS&\bf{57.84}&\bf{83.57}&\bf{60.62}&82.59&90&83.38\\
			AIFeynman&55.78&27.14&52.69&78.51&35.71&73.9\\
			GP-GOMEA&26.83&29.46&27.12&71.55&71.43&71.54\\
			AFP\_FE&26.98&20&26.23&59.05&28.57&55.77\\
			ITEA&22.41&7.14&20.77&27.59&21.43&26.93\\
			AFP&21.12&15.18&20.48&44.83&25&42.69\\
			DSR&19.72&19.64&19.71&25&14.29&23.85\\
			Operon&16.55&11.43&16&86.21&\bf{92.86}&86.93\\
			gplearn&16.27&8.93&15.48&32.76&7.14&30\\
			SBP-GP&12.72&11.61&12.6&73.71&78.57&74.23\\
			EPLEX&12.39&8.93&12.02&46.98&21.43&44.23\\
			BSR&2.48&0.89&2.31&10.78&21.43&11.93\\
			FEAT&0&0.89&0.1&39.66&42.86&40\\
			FFX&0&0&0&0&0&0\\
			MRGP&0&0&0&\bf{93.1}&89.29&\bf{92.69}\\
			\hline
		\end{tabular}
\end{table}
